---
title: "flat_first.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
datafile <- system.file("day1_universe.csv", package = "LocationTimeSampling")
day1_universe <- read.csv(datafile, encoding = "UTF-8")

day1_universe
```


# Build the configuration file for time location

# lts_setup
    
```{r function-lts_setup}
#' lts_setup
#' 
#' Apply a factorial design on all potential combination of time and location -
#' includes the possibiity to add ad-hoc constraints
#' 
#' The function will save an xlsform to be used for data collection
#'  preconfigured with the required  data universe
#' 
#' @param location (Bus terminal), point (bus gate) and 
#' @param time (timeshedule for bus).
#' @param constraint restriction ad-hic
#' @param filepath to save the xlsform 
#' @return result will be a list that will include all valid time/location combination within a day 
#' 
#' @export
lts_setup <- function(){
    
}
```
  
```{r example-lts_setup}
lts_setup()
```
  
```{r tests-lts_setup}
test_that("lts_setup works", {
  expect_true(inherits(lts_setup, "function")) 
})
```
  



# Sample data collection shift - aka an assignement for one person at one time for one location

# lts_sample_shift
    
```{r function-lts_sample_shift}
#' lts_sample_shift
#' 
#' Draw the sample of ata collection shift to perform from the full 
#' location time universe 
#' 
#' NEXT - if stratified sampling then need to input data collected from previous
#'  shift - this will allow to calculate weight to apply for the next shift
#'   during the extrapolation
#' @param config_path path to the the configuration file
#' @param sample_size sample size neeeded
#' @param start_date enforce mdy "11-01-23"
#' @param end_date  enforce mdy  "11-30-23"
#' @param strata "low" "mid-low" "mid-high" "high" if strata is NULL then default is "low"
#' @param filename file to save the output 
#' @return selection of specific shift selected as sample (day / time / terminal / gate )
#' 
#' @export
lts_sample_shift <- function(config_path,
                             sample_size = 400,
                             start_date, 
                             end_date,
                             strata = "low",
                             filename){
  

 
config <-   readxl::read_excel(config_path, sheet = 1) |> 
  tidyr::separate(segment, 
                  into = c("terminal", "gate", "timeperiod"), 
                  sep = " - ")
  
universe <- 
  tidyr::expand_grid(day = lubridate::as_date(lubridate::mdy(start_date):lubridate::mdy(end_date)), 
 # tidyr::expand_grid(day = lubridate::make_date(2023, 11, 01:30), 
              config) |> 
  dplyr::transmute(day, timeperiod, terminal, gate,
            schedule = timeperiod,
            start = stringr::str_match(schedule, "^(.+?).00")[,2], 
            end = stringr::str_match(schedule, "a (.+).00$")[,2], 
            mid_schedule = (as.numeric(start) + as.numeric(end)) / 2) |> 
  dplyr::arrange(day, timeperiod, terminal, gate)

#sample_size <- 400 # turns for the whole month
srs_sample_size <- sample_size * .2
sys_sample_size <- sample_size * .8 # based on the June pilot

systematic_sample <- function(.x, n) {
  random_offset <- sample(nrow(.x)/n, 1)
    sampled_turns <- .x[round(seq(random_offset, 
                                  nrow(.x), 
                                  by = (nrow(.x)/n)), 0),]
}


# this is kosher for now, but we should do it differently in the future...
split_srs <- universe |> 
                dplyr::filter(strata == "low")

split_sys <- dplyr::anti_join(universe, split_srs)

sampled_turns_srs <- split_srs |> 
                      dplyr::arrange(day, timeperiod, terminal, gate) |>
                      systematic_sample(srs_sample_size)

sampled_turns_sys <- split_sys |> 
  systematic_sample(n = round(sys_sample_size, 0)) |> 
  dplyr::arrange(day, timeperiod, terminal, gate)

sampled_turns <- dplyr::bind_rows(sampled_turns_srs, sampled_turns_sys) |> 
                 dplyr::arrange(day, timeperiod, terminal, gate)

# check that the workload is distributed almost equally over the course of the month
#cat(sampled_turns |> dplyr::count(day) |> dplyr::count(n))

# month = substr(sampled_turns$day,6,7)
# year = substr(sampled_turns$day,1,4)
# today=today()
# export file
# filename <- paste(today," ", month, "-", year, "-", "(pps)", "timeperiods Conteo Tacna_.xlsx")
writexl::write_xlsx(sampled_turns, path=filename) 
    
}
```
  
```{r example-lts_sample_shift}
## day1_universe.xlsx
config_path <- system.file("day1_universe.xlsx", package = "LocationTimeSampling")


lts_sample_shift(config_path,
                 sample_size = 400,
                 start_date = "11-01-23", 
                 end_date = "11-30-23",
                 strata = "low",
                 filename = "sampleshift.xlsx")
```
  
```{r tests-lts_sample_shift}
test_that("lts_sample_shift works", {
  expect_true(inherits(lts_sample_shift, "function")) 
})
```
  

# An enumerator allocation function

Assigning to enumerator each of the shift selected within the sample based on their availability


# Extrapolate the data collection results to obtain total population estimation
# lts_extrapolate_numbers
    
```{r function-lts_extrapolate_numbers}
#' Title
#' 
#' Description
#' 
#' @param location/point
#' @param time
#' @param day
#' @param number
#' @param weight
#' 
#' @return a list including weekly estimates of entry and exist 
#'            together a visual barchart and  line chart  
#' 
#' @export
lts_extrapolate_numbers <- function(){
    
  
  
}
```
  
```{r example-lts_extrapolate_numbers}
lts_extrapolate_numbers()
```
  
```{r tests-lts_extrapolate_numbers}
test_that("lts_extrapolate_numbers works", {
  expect_true(inherits(lts_extrapolate_numbers, "function")) 
})
```
  
 
 
<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_first.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
